\sysfull

### 2018-04-17 paper/implementation.tex
impl: specify mcu

Page tagging imposes a data alignment requirement.
Page size $S$ must be a power of two. 
%
Pages must be aligned to an $S$-byte boundary. 
%
We experimented with 32-, 64-, 128- and 256-byte pages, an 8kB non-volatile \texttt{\underline{shadow}} buffer and
an 8kB non-volatile \texttt{\underline{store}}, and a volatile working buffer
of 1kB, which is half of the total SRAM size. 
%\begin{figure}
%	\centering
%	\includegraphics[width=\textwidth]{figures/graffle/paging.pdf}
%	\caption{Illustration of \sys page tags mechanism.}
%	\label{figure:coala_page_tags}
%\end{figure}

>>>>

Page tagging imposes a data alignment requirement.
Page size $S$ must be a power of two. 
%
Pages must be aligned to an $S$-byte boundary. 
%
We experimented with 32-, 64-, 128- and 256-byte pages, an 8kB non-volatile \texttt{\underline{shadow}} buffer and
an 8kB non-volatile \texttt{\underline{store}}, and a volatile working buffer
of 1kB, which is half of the total SRAM size in the MSP430FR6989 microcontroller.
%\begin{figure}
%	\centering
%	\includegraphics[width=\textwidth]{figures/graffle/paging.pdf}
%	\caption{Illustration of \sys page tags mechanism.}
%	\label{figure:coala_page_tags}
%\end{figure}
